Demes: a specification for interchanging complex demography

### 2021-06-17 paper.tex
Add notes on GUIs

    \item
    % https://github.com/popsim-consortium/demes-paper/issues/11
    We should mention coasim~\citep{mailund2005coasim} because its model
    seems quite close to what we have. It's not suitable as a standard though
    because it uses a programming language.

>>>>

    \item
    % https://github.com/popsim-consortium/demes-paper/issues/11
    We should mention coasim~\citep{mailund2005coasim} because its model
    seems quite close to what we have. It's not suitable as a standard though
    because it uses a programming language. Besides coasim, there was
    PopPlanner~\citep{ewing2010msms}
    (a Java GUI which allows the user to build models
    graphically and export the corresponding \ms\ command lines)
    and MODELER4SIMCOAL2~\citep{antao2007modeler4simcoal2}
    (a webapp that provided a set of common model templates that could be
    parameterised to output the corresponding simcoal input files.)
    \jkcomment{Not sure where these fit into the narrative, just
    summarising here for later reference}.
